Isabelle/C/Clean - A Show-Case for a Semantic Back-End for Isabelle/C

### 2019-10-29 C11-BackEnds/Clean_wrapper/document/root.tex
added another example and a first shot for doc generation of Isabelle/C/Clean

\title{Clean - An Abstract Imperative Programming Language and its Theory}
\author{%
  \href{https://www.lri.fr/~ftuong/}{Fr\'ed\'eric Tuong}
  \and
  \href{https://www.lri.fr/~wolff/}{Burkhart Wolff} \\
  \and
  (with Contributions of \href{https://www.lri.fr/~keller/}{Chantal Keller})}
\publishers{%
  \mbox{LRI, Univ. Paris-Sud, CNRS, Universit\'e Paris-Saclay} \\
  b\^at. 650 Ada Lovelace, 91405 Orsay, France \texorpdfstring{\\}{}
}

@@

\begin{abstract}
Clean is based on a simple, abstract execution model for an imperative target language. ``Abstract''
is understood as contrast to ``Concrete Semantics''; alternatively, the term ``shallow-style
embedding'' could be used. It strives for a type-safe notation of program-variables, an incremental
construction of the typed state-space, support of incremental verification, and 
open-world extensibility of new type definitions being intertwined with the program
definition.

Clean is based on a ``no-frills'' state-exception monad with the usual definitions of \isa{bind} and
\isa{unit} for the compositional glue of state-based computations. Clean offers conditionals and
loops supporting C-like control-flow operators such as \isa{break} and \isa{return}. The state-space
construction is based on the extensible record package. Direct recursion of procedures is supported.

Clean's design strives for extreme simplicity. It is geared towards symbolic execution and proven
correct verification tools. The underlying libraries of this package, however, deliberately restrict
themselves to the most elementary infrastructure for these tasks. The package is intended to serve
as demonstrator semantic backend for Isabelle/C~\cite{TuongWolff19}, or for the test-generation
technique described in~\cite{DBLP:conf/tap/Keller18}.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \input{session}
\newpage
\input{Clean.tex}

\input{Quicksort_concept.tex}
\input{SquareRoot_concept.tex}

\newpage
\chapter{Appendix : Used Monad Libraries}
\input{MonadSE.tex}
\input{Seq_MonadSE.tex}
\input{Symbex_MonadSE.tex}
\input{Clean_Symbex.tex}
\input{Test_Clean.tex}
\input{Hoare_MonadSE.tex}
\input{Hoare_Clean.tex}

>>>>

\title{Isabelle/C/Clean - A Show-Case for a Semantic Back-End for Isabelle/C}
\author{%
  \href{https://www.lri.fr/~ftuong/}{Fr\'ed\'eric Tuong}
  \and
  \href{https://www.lri.fr/~wolff/}{Burkhart Wolff}}
\publishers{%
  \mbox{LRI, Univ. Paris-Sud, CNRS, Universit\'e Paris-Saclay} \\
  b\^at. 650 Ada Lovelace, 91405 Orsay, France \texorpdfstring{\\}{}
}

@@

\begin{abstract}
Isabelle/C ~\cite{TuongWolff19} is a C11 ~front-end for Isabelle/PIDE providing 
generic support for C parsing, editing, and highlighting. Isabelle/C also provides 
a generic interface for semantic interpretations of the C11 programs and program
fragments. In particular, Isabelle/C also offers the generic framework
to define \emph{annotation commands} and \emph{C antiquotations} 
that can be custumized to a specific semantic back-end.

Clean is such a semantic back-end, i.e. an Isabelle theory providing a
semantics and execution model. Clean is an abstract, ``shallow-style embedding''  
for an imperative core language. It strives for a type-safe notation of 
program-variables, an incremental construction of the typed state-space, 
support of incremental verification, and  open-world extensibility of new 
type definitions being intertwined with the program definitions.

Clean is based on a ``no-frills'' state-exception monad with the usual definitions 
of \isa{bind} and \isa{unit} for the compositional glue of state-based computations. 
Clean offers conditionals and loops supporting C-like control-flow operators such 
as \isa{break} and \isa{return}. The state-space construction is based on the 
extensible record package. Direct recursion of C-functions is supported.

The current session instantiates Isabelle/C with Clean and produces the 
Isabelle/C/Clean instance. It is conceived as a demonstrator for creating
other instances of Isabelle/C with other semantic backends such as AutoCorres
~\cite{DBLP:conf/pldi/GreenawayLAK14},
IMP2~\cite{DBLP:journals/afp/LammichW19} or Orca~\cite{bockenek:hal-02069705}.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \input{session}
\newpage

%\newpage
%\chapter{Appendix : Used Monad Libraries}
\input{Backend.tex}				
\input{Clean.tex}				
\input{Core.tex}				
\input{Generator_dynamic_sequential.tex}	
\input{Init.tex}				
\input{Isabelle_code_runtime.tex}
%\input{Isabelle_typedecl.tex}
%\input{Meta_C.tex}
